Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-01-28 manuscript/manuscript.tex
ms updates

@@

\begin{align}
  \label{eq:}
  {N}_{e}(x) &= \exp \left( -\frac{V(x)}{2} Q^2(x) \right) & \text{\emph{effective population equation}} \\
  {R}(x) &= \frac{4NU s}{\exp(4 N s)-1}  & \text{\emph{ratchet equation}} 
\end{align}

@@

\begin{align}
  V(x) &= U s - 2 {R}(x) s & \text{\emph{variation equation}} \\
  Q^2(x) &= \frac{2}{(1-Z)(2-(2-M)Z)} & \text{\emph{linkage persistence factor}} \\
  Z &= 1 - \frac{Us}{U-{R(x)}} & \text{\emph{}} \text{\emph{variance decay rate}}
\end{align}

>>>>

\begin{abstract}

Previous work in population genomics has established that negative selection
against against new deleterious variants introduced by mutation profoundly
shapes large-scale patterns of variation across the genome. However, the
mathematical models that describe this process only consider variants so
deleterious that they cannot drift up in frequency and ultimately fix. In
reality, there number of mildly deleterious mutations

\end{abstract}

@@

\begin{align}
  \label{eq:}
  {N}_{e}(x) &= N \exp \left( -\frac{V(x)}{2} Q^2(x) \right) & \text{\emph{effective population equation}} \\
  {R}(x) &= \frac{4N_e(x)U s}{\exp(4 N_e(x) s)-1}  & \text{\emph{ratchet equation}} 
\end{align}

@@

\begin{align}
  V(x) &= U s - 2 {R}(x) s & \text{\emph{fitness variance equation}} \\
  Q^2(x) &= \frac{2}{(1-Z)(2-(2-M)Z)} & \text{\emph{linkage inflation factor}} \\
  Z &= 1 - \frac{Us}{U-{R(x)}} & \text{\emph{}} \text{\emph{variance decay rate}}
\end{align}
